\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE 1
%====================
\subsection{{Tech Lead – Backend \& Distributed Systems \hfill Jul 2025 - Present}}
\subtext{Quantum Leap \hfill Setúbal, Portugal (Remote)}
\begin{zitemize}
\item Led backend engineering team through critical architectural transformations. 
\item Solved video processing latency issues by implementing intelligent caching systems.
\item Pioneered AI-powered solutions for automated SQL generation and data visualization.
\item Built comprehensive monitoring infrastructure with Prometheus/Grafana for improved system observability.
\item Restructured team organization while mentoring engineers and establishing best practices.
\item Architected distributed systems leveraging Elixir/Erlang, RabbitMQ, and MQTT for reliable event-driven architectures on AWS.
\end{zitemize}

%====================
% EXPERIENCE 2
%====================
\subsection{{Senior Data Specialist \hfill Dec 2023 - Jun 2025}}
\subtext{Ministry of Health of Brazil \hfill Brasília, DF, Brazil (Remote)}
\begin{zitemize}
\item Designed and optimized national-level data pipelines for public health analytics.
\item Led the implementation of scalable solutions using Python, SQL, Airflow, and Spark to support real-time decision-making during health crises.
\item Contributed to the strategic integration of data across systems to enhance reporting and policy formulation.
\end{zitemize}

%====================
% EXPERIENCE 3
%====================
\subsection{{Data Engineer Specialist \hfill Apr 2023 - Jul 2024}}
\subtext{Ministry of Health of Brazil \hfill Brasília, DF, Brazil (Remote)}
\begin{zitemize}
\item Responsible for data analysis at CGMAIA (General Coordination of Monitoring, Evaluation, and Analytical Intelligence).
\item Delivered analytical reports for demands across Brazil, and created dashboards for indicators and project monitoring.
\item Utilized tools including Python, SQL, R, Airflow, Superset, and others.
\end{zitemize}

%====================
% EXPERIENCE 4
%====================
\subsection{{Back End Developer \hfill Aug 2022 - Mar 2023}}
\subtext{Stone Co. \hfill Rio de Janeiro, Brazil (Remote)}
\begin{zitemize}
\item Worked as a backend developer using the Elixir programming language.
\item Assisted in structuring Payment Account Settlement, creating dashboards and reports for incident identification.
\end{zitemize}

%====================
% EXPERIENCE 5
%====================
\subsection{{Data Engineer Leader \hfill Mar 2020 - Aug 2022}}
\subtext{LAIS - Laboratory of Technological Innovation in Health \hfill Rio Grande do Norte, Brazil (Part-time Remote)}
\begin{zitemize}
\item Responsible for data analysis (Data Scientist) and forecasting health systems.
\item Analyzed COVID-19 data, assisting decision-making in various states of Brazil.
\item Served as the backend leader for some solutions developed in Python using Django.
\end{zitemize}

\newpage

%====================
% EXPERIENCE 6
%====================
\subsection{{Google Certified Trainer \hfill May 2018 - Jun 2023}}
\subtext{Google for Education \hfill Brazil}
\begin{zitemize}
\item Traveled extensively across Brazil helping diverse institutions adopt Google solutions for educational and business transformation.
\item Trained over 10,000 teachers, administrators, and corporate teams to optimize their workflows using Google Workspace tools.
\item During the pandemic, played a crucial role in Brazil's digital education transformation, including partnering with the Brasília government to implement large-scale remote learning initiatives.
\item Led workshops and training sessions nationwide, empowering educators to transition from traditional to digital classrooms.
\end{zitemize}

%====================
% EXPERIENCE 7
%====================
\subsection{{Director of Technology \hfill Mar 2019 - Jun 2022}}
\subtext{Ensinar Tecnologia \hfill Recife, Brazil (Part-time Remote)}
\begin{zitemize}
\item Worked as a technology and innovation manager in educational projects across Brazil.
\item Collaborated with companies like Google (implementation of the Google for Education program) and Microsoft (AcademIA Microsoft AI project).
\item Responsible for all innovation management and customer support.
\end{zitemize}

%====================
% EXPERIENCE 8
%====================
\subsection{{Professor \hfill Jun 2017 - Nov 2017 and Apr 2018 - Mar 2020}}
\subtext{Federal University of Sergipe \hfill São Cristóvão, SE}
\begin{zitemize}
\item Computer Science professor, specializing in languages.
\item Taught courses in Compilers, Formal Languages, Functional Programming, Imperative Programming, Object-Oriented Programming, Data Structures, and Fundamentals of Computing.
\end{zitemize}

%====================
% EXPERIENCE 9
%====================
\subsection{{Director of Technology \hfill Feb 2016 - Mar 2020}}
\subtext{COESI \hfill Aracaju, Brazil}
\begin{zitemize}
\item Served as technology coordinator, helping to create robotics projects and teaching programming, as well as corporate solutions.
\end{zitemize}

%====================
% EXPERIENCE 11
%====================
\subsection{{Computer Science Intern \hfill Nov 2015 - Aug 2016}}
\subtext{Ministry of Labor Prosecution Office \hfill Aracaju, Brazil}
\begin{zitemize}
\item Gained experience in computer science applications within government operations.
\end{zitemize}

%====================
% EXPERIENCE 12
%====================
\subsection{{Computer Science Intern \hfill Apr 2015 - Oct 2015}}
\subtext{Correios \hfill Aracaju, Brazil}
\begin{zitemize}
\item Applied computer science knowledge in postal service operations and systems.
\end{zitemize}

\end{document}